---
title: ""
subtitle: ""
author: "Andrej Sokolič"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

<!-- --------------------------------------- ->
<!-- Naslednji del predstavlja CSS oblikovanje -->

<style type="text/css">
<!-- body p { -->
<!--   color: #000000; -->
<!-- } -->

slides > slide {
font-family: 'Arial';
}
ul {
  display: block;
  font-size: 30px;
  margin-top: 0;
  margin-bottom: 0;
  margin-left: 0;
  margin-right: 0;
  color: #494949;
}


.title-slide hgroup h1 {
  color: black;
}

.title-slide hgroup h2 {
  color: black;
}

.title-slide hgroup p {
  font-size: 24px;
  color: #494949;
  font-weight: bold;
}

slides > slide > hgroup h2 {
  color: black;
}

#ID > p { 
  margin-top: -50px; 
} 

/* spodaj da je lahko tabela in slika levo desno */

.twoC {width: 100%} 
.clearer {clear: both}
.twoC .table {max-width: 50%; float: right}
.twoC img {max-width: 50%; float: left}

.levo img {
  max-width: 50%;
  float:left;
  margin-top: -50px;
  margin-left: -20px;
}

.desno img {
  max-width: 50%;
  float:right;
  margin-top: 50px;
  margin-left: -20px;
}
</style>

<!-- --------------------------------------- ->
<!-- Začetek dokumenta -->

```{r LIBs, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = FALSE,  fig.align='center')

```

```{r DATA, warning=FALSE, include=F}

```



## Uvod



## Uporabi ID definiran v CSS {#ID}



<p class = "levo">


</p>

<p class = "desno">

</p>



## AA

<div float: center>

</div>

<!-- Prazen slajd -->
***
